Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-04-27 02_paper/02_study/paper_methods.Rmd
method update
method paper new table

floatsintext      : yes
figsintext        : yes
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

```{r include=FALSE}
#install.packages("needs")

@@

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable)
```

@@

# select relevant columns from first questionnaire 
demo.data <- quest.data %>% dplyr::select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05,
                                  LI10_05,
                                  LI11_01,
                                  LI13_01,
                                  LI14,
                                  LI18,
                                  LI16_05,
                                  LI17
                                  )

# rename columns
demo.data <- rename(demo.data, c("Group" = "LI06_05",
                                 "Gender" = "LI02_01_1",
                                 "Age" = "LI03_01",
                                 "Teaching Experience" = "LI04_01",
                                 "Type of School" = "LI18",
                                 "Grade" = "LI16_05",
                                 "Subject" = "LI10_05",
                                 "Semester" = "LI11_01",
                                 "Internship" = "LI13_01",
                                 "Extracurricular Teaching Experience" = "LI14",
                                 "Secondary Teaching Activities" = "LI17"
                                 ))

@@

# creating new column with percentage of gender
demo.data <- demo.data %>%
  group_by(Group) %>%
  mutate(Gender_Sum=n())

@@

# create new columns that give proportion of Gender
# percentage = female gender divided by all female Gender
# demo.data <- demo.data  %>% 
#   group_by(Group) %>% 
#   mutate(Gender_percentage = Gender/Gender_Sum) %>% 
#   mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percentage" = round(sum(Gender/Gender_Sum) * 100, digits = 1),
            "M Age in years" = round(mean(Age), 1),
            "SD Age in years" = round(sd(Age), 1),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
            "M Exp. in years" = round(mean(`Teaching Experience`), 1),
            "SD Exp. in years" = round(sd(`Teaching Experience`), 1),
            "Min Exp. in years" = min(`Teaching Experience`),
            "Max Exp. in years" = max(`Teaching Experience`),
            "M Semester" = round(mean(Semester), 1),
            "SD Semester" = round(sd(Semester), 1),
            "Min Semester" = min(Semester),
            "Max Semester" = max(Semester),
            "M Internship in teaching units" = round(mean(Internship), 1),
            "SD Internship in teaching units" = round(sd(Internship), 1),
            "Min Internship in teaching units" = min(Internship),
            "Max Internship in teaching units" = max(Internship),
            "Extracurricular Teaching Experience in percentage" = round(sum(`Extracurricular Teaching Experience`/Gender_Sum) * 100, digits = 1),
            "Secondary Teaching Activities in percentage" = round(sum(`Secondary Teaching Activities`/Gender_Sum) * 100)
           )

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r demo.table %>% filter(Group == "Expert") %>% pull("M Exp. in years") %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Exp. in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Exp. in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Exp. in years")`). `r demo.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities in percentage")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Exp. in years") %>% mean() %>% round(., digits = 1)` years. On average, the student teachers were in their `r demo.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`). Furthermore, they had an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Internship in teaching units") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Internship in teaching units") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Internship in teaching units")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Internship in teaching units")`) through the internships during their studies. `r demo.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience in percentage")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

```{r presence_questionnaire, include=TRUE, echo=FALSE, results='asis'}

# select relevant columns
quest.data <- quest.data %>% dplyr::select(LM01_01:LO01_02, LI06_05)

# rename columns
quest.data <- rename(quest.data, c("Group" = "LI06_05"))

# define expert and novice with ifelse function
quest.data$Group = ifelse(quest.data$Group < 200, "Novice","Expert")

# creating a matrix
quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
rownames(quest.table) <- c("LM", "LB", "LP", "LV")
  colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")

@@

loop.data <- quest.data %>% 
  dplyr::select(starts_with(match = i))

quest.table[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  mean() %>% 
  round(., digits = 2) ->
quest.table[i, "M"]

# calculating SD
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  sd() %>% 
  round(., digits = 2) ->
quest.table[i, "SD"]

# calculating Min
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  min() %>% 
  round(., digits = 2) ->
quest.table[i, "Min"]

# calculating Max
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  max() %>% 
  round(., digits = 2) ->
quest.table[i, "Max"]

# calculating Skewness
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  skewness() %>% 
  round(., digits = 2) ->
quest.table[i, "Skewness"]

# calculating Kurtosis
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  kurtosis() %>% 
  round(., digits = 2) ->
quest.table[i, "Kurtosis"]

# calculating alpha
alpha <- loop.data %>% 
  cronbach.alpha() 
alpha$alpha

quest.table[i, "alpha"] <- round(alpha$alpha,2)

@@

# rename columns 
rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

# format and insert table in manuscript
papaja::apa_table(
quest.table,
  caption = "Scale analysis for teachers' self-assessment",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package

# Classroom Management

@@

>>>>

floatsintext      : no
figsintext        : yes
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

```{r include=FALSE}
# install.packages("needs")

@@

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable)

@@

# read in data and select and rename relevant columns with transmute 
demo.data <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  transmute(Group = LI06_05,
                                 Gender = LI02_01_1,
                                 Age = LI03_01,
                                 `Teaching Experience` = LI04_01,
                                 `Type of School` = LI18,
                                 Grade = LI16_05,
                                 Subject = LI10_05,
                                 Semester = LI11_01,
                                 Internship = LI13_01,
                                 `Extracurricular Teaching Experience` = LI14,
                                 `Secondary Teaching Activities` = LI17
                                 )

@@

# creating new column with percent of gender
demo.data <- demo.data %>%
  group_by(Group) %>%
  mutate(Gender_Sum=n())

@@

# create new columns that give proportion of Gender
# percent = female gender divided by all female Gender
# demo.data <- demo.data  %>% 
#   group_by(Group) %>% 
#   mutate(Gender_percent = Gender/Gender_Sum) %>% 
#   mutate(Gender_percent = round(sum(Gender_percent)*100, digits=0))

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percent" = round(sum(Gender/Gender_Sum) * 100, digits = 1),
            "M Age in years" = round(mean(Age), 1),
            "SD Age in years" = round(sd(Age), 1),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
            "M Exp. in years" = round(mean(`Teaching Experience`), 1),
            "SD Exp. in years" = round(sd(`Teaching Experience`), 1),
            "Min Exp. in years" = min(`Teaching Experience`),
            "Max Exp. in years" = max(`Teaching Experience`),
            "M Semester" = round(mean(Semester), 1),
            "SD Semester" = round(sd(Semester), 1),
            "Min Semester" = min(Semester),
            "Max Semester" = max(Semester),
            "M Internship in teaching units" = round(mean(Internship), 1),
            "SD Internship in teaching units" = round(sd(Internship), 1),
            "Min Internship in teaching units" = min(Internship),
            "Max Internship in teaching units" = max(Internship),
            "Extracurricular Teaching Experience in percent" = round(sum(`Extracurricular Teaching Experience`/Gender_Sum) * 100, digits = 1),
            "Secondary Teaching Activities in percent" = round(sum(`Secondary Teaching Activities`/Gender_Sum) * 100)
           )

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r demo.table %>% filter(Group == "Expert") %>% pull("M Exp. in years") %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Exp. in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Exp. in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Exp. in years")`). `r demo.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities in percent")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Exp. in years") %>% mean() %>% round(., digits = 1)` years. On average, the student teachers were in their `r demo.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`). Furthermore, they had an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Internship in teaching units") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Internship in teaching units") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Internship in teaching units")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Internship in teaching units")`) through the internships during their studies. `r demo.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience in percent")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

```{r presence_questionnaire_novices, include=TRUE, echo=FALSE, results='asis'}
# load data files
quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
  mutate(Group = ifelse(LI06_05 < 200, "Novice","Expert")) %>% 
  dplyr::select(Group, LM01_01:LO01_02)

# create two data frames
quest.data.novice <- quest.data %>% filter(Group == "Novice")
quest.data.expert <- quest.data %>% filter(Group == "Expert")

############## NOVICE TABLE #########################

# creating a matrix
quest.table.novice <- matrix(data = NA, nrow = 4, ncol = 8)
rownames(quest.table.novice) <- c("LM", "LB", "LP", "LV")
  colnames(quest.table.novice) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")

@@

loop.data <- quest.data.novice %>% 
  dplyr::select(starts_with(match = i))

quest.table.novice[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  mean() %>% 
  round(., digits = 2) ->
quest.table.novice[i, "M"]

# calculating SD
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  sd() %>% 
  round(., digits = 2) ->
quest.table.novice[i, "SD"]

# calculating Min
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  min() %>% 
  round(., digits = 2) ->
quest.table.novice[i, "Min"]

# calculating Max
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  max() %>% 
  round(., digits = 2) ->
quest.table.novice[i, "Max"]

# calculating Skewness
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  skewness() %>% 
  round(., digits = 2) ->
quest.table.novice[i, "Skewness"]

# calculating Kurtosis
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  kurtosis() %>% 
  round(., digits = 2) ->
quest.table.novice[i, "Kurtosis"]

# calculating alpha
alpha <- loop.data %>% 
  cronbach.alpha()

quest.table.novice[i, "alpha"] <- round(alpha$alpha,2)

@@

# rename columns 
rownames(quest.table.novice) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

# format and insert table in manuscript
papaja::apa_table(
quest.table.novice,
  caption = "Scale analysis for novices' self-assessment",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)
```

```{r presence_questionnaire_experts, include=TRUE, echo=FALSE, results='asis'}

############## EXPERT TABLE #########################

# creating a matrix
quest.table.expert <- matrix(data = NA, nrow = 4, ncol = 8)
rownames(quest.table.expert) <- c("LM", "LB", "LP", "LV")
  colnames(quest.table.expert) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")

loop.data <- quest.data.expert %>% 
  dplyr::select(starts_with(match = i))

quest.table.expert[i, "N Items"] <- length(loop.data)

# calculating mean
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  mean() %>% 
  round(., digits = 2) ->
quest.table.expert[i, "M"]

# calculating SD
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  sd() %>% 
  round(., digits = 2) ->
quest.table.expert[i, "SD"]

# calculating Min
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  min() %>% 
  round(., digits = 2) ->
quest.table.expert[i, "Min"]

# calculating Max
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  max() %>% 
  round(., digits = 2) ->
quest.table.expert[i, "Max"]

# calculating Skewness
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  skewness() %>% 
  round(., digits = 2) ->
quest.table.expert[i, "Skewness"]

# calculating Kurtosis
loop.data %>% 
  mutate(mean = rowMeans(.)) %>% 
  pull(mean) %>% 
  kurtosis() %>% 
  round(., digits = 2) ->
quest.table.expert[i, "Kurtosis"]

# calculating alpha
alpha <- loop.data %>% 
  cronbach.alpha()

quest.table.expert[i, "alpha"] <- round(alpha$alpha,2)

# rename columns 
rownames(quest.table.expert) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")

# format and insert table in manuscript
papaja::apa_table(
quest.table.expert,
  caption = "Scale analysis for experts' self-assessment",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
)

@@

```{r item_analysis_classroom_management, include=TRUE, results='asis'}
quest.data %>% 
  dplyr::select(contains("LM")) %>% 
  as.data.frame() %>% 
  tab_itemscale(CSS = list(
    css.firsttablerow.col7 = "'cronbachs alpha';"
  ))
```

```{r item_analysis_balance, include=TRUE}
# quest.data %>% 
#   dplyr::select(contains("LB")) %>% 
#   as.data.frame() %>% 
#   tab_itemscale()
```

### 2022-04-27 02_paper/02_study/paper_methods.tex
method paper new table

@@

@@

All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{knitr} (Version 1.38; Xie, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.

@@

@@

>>>>

\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:demographicstable}Demographic Information and Teaching Experience}

\tiny{

\begin{tabular}{lllllllllllllllllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years} & \multicolumn{1}{c}{M Exp. in years} & \multicolumn{1}{c}{SD Exp. in years} & \multicolumn{1}{c}{Min Exp. in years} & \multicolumn{1}{c}{Max Exp. in years} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship in teaching units} & \multicolumn{1}{c}{SD Internship in teaching units} & \multicolumn{1}{c}{Min Internship in teaching units} & \multicolumn{1}{c}{Max Internship in teaching units} & \multicolumn{1}{c}{Extracurricular Teaching Experience in percent} & \multicolumn{1}{c}{Secondary Teaching Activities in percent}\\
\midrule
Expert & 7 & 71.40 & 45.10 & 12.00 & 27.00 & 59.00 & 18.10 & 14.10 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 71.00\\
Novice & 21 & 61.90 & 23.30 & 1.70 & 20.00 & 27.00 & 0.00 & 0.00 & 0.00 & 0.00 & 7.40 & 2.50 & 3.00 & 11.00 & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

@@

\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:presence_questionnaire_novices}Scale analysis for novices' self-assessment}

\tiny{

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
\midrule
Classroom Management & 8.00 & 2.94 & 0.26 & 2.50 & 3.38 & 0.02 & 1.69 & 0.31\\
Balance & 3.00 & 3.14 & 0.56 & 1.67 & 4.00 & -0.45 & 3.53 & 0.71\\
Presence & 8.00 & 3.10 & 0.36 & 2.50 & 3.88 & 0.10 & 2.65 & 0.66\\
Natural Behavior & 3.00 & 3.17 & 0.65 & 1.67 & 4.00 & -0.65 & 2.91 & 0.80\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:presence_questionnaire_experts}Scale analysis for experts' self-assessment}

\tiny{

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
\midrule
Classroom Management & 8.00 & 3.00 & 0.20 & 2.75 & 3.25 & 0.25 & 1.42 & -0.16\\
Balance & 3.00 & 3.43 & 0.42 & 2.67 & 4.00 & -0.57 & 2.87 & 0.41\\
Presence & 8.00 & 3.36 & 0.45 & 2.50 & 3.88 & -0.85 & 2.95 & 0.84\\
Natural Behavior & 3.00 & 3.38 & 0.36 & 3.00 & 4.00 & 0.60 & 2.36 & 0.00\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

Component 1

Missings

Mean

SD

Skew

Item Difficulty

Item Discrimination

α if deleted

0.00 \%

3.32

0.72

-0.58

0.83

0.18

0.10

0.00 \%

3.32

0.55

0.06

0.83

0.08

0.19

0.00 \%

3.36

0.56

-0.07

0.84

-0.06

0.26

0.00 \%

3.18

0.67

-0.22

0.79

0.25

0.05

0.00 \%

2.32

0.61

-0.29

0.77

0.00

0.23

0.00 \%

2.21

0.63

0.77

0.55

-0.30

0.41

0.00 \%

2.96

0.58

-0.01

0.74

0.33

0.02

0.00 \%

2.96

0.69

-0.67

0.74

0.21

0.08

Mean inter-item-correlation=0.028 · Cronbach's α=0.207

@@

All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-xtable}{}}%
Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to LaTeX or HTML}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
